\ourlongtitle

### 2021-08-27 Bernoulli/AnswerReviews.tex

We would like to thank the associate editor and the referees for the attention they paid to our work and for their positive feedbacks.

\bigskip

Minor errors and typos listed by R2 were corrected as suggested. Please find below a few detailed answers.

\begin{itemize}
\item It might have made the paper less scary and dry to read to first provide standard setups (along the lines of what is at the top of p.2), then proceed to the objective (formula (1.2)) and only then supplement all the measure-theoretic setup, e.g. as part of section 2. This would also have yielded the advantage of collecting mathematical notation at the start of section 2 (Is a collection of common notation in tabular form allowed in Bernoulli? This would be a friendly service to the reader.) rather than scattering it over the start of section 1 and section 2.\\
{\em We thank the referee for this suggestion. We postponed the introduction of (1.2)  and the objective of the paper (additive smoothing) after the standard setups (Feynman-Kac path models and hidden Markov models) for better clarity.}
\item p.7 (2.10) and elsewhere uses rectangular brackets as in $\phi_m[\ell_m(\cdot,x_{m+1})]$ which I think is meant to denote $\int_{X_m}\ell_m(x_m,x_{m+1})\phi_m(dx_m)$. This notation has not been introduced. The "Preliminaries" at the top of p.4 have $\mu h$ for the integral of a function $h$ against a measure $\mu$ which would suggest $\phi_m \ell(\cdot,x_{m+1})$. Since the rectangular brackets are used in this sense at many points in the paper, perhaps this notation should be added to the preliminaries.\\
{\em }
\item p.7 Just before 2.2.2, it would be nice to comment on where one might get suitable adjustment weights $\vartheta_n$ from. How are these to be chosen or tuned?\\
{\em We added the following lines after the introduction of the adjustment-weight function (after (2.8): "Adjustment multiplier weights were introduced in [31] to propose data-driven proposal distributions and design robust filtering estimates. These weights usually depend on the new observation and are often chosen to approximate the predictive likelihood of the new observation given the current particle. For further discussions see for instance [7,Chapter~8]".}
\item p. 15-16: for the presentation of Example 2, I feel it would be better to describe the problem fully before giving Durham and Gallant's solution.\\
{\em Do not agree!}
\item p.29 Appendix A in the supplement has $\phi_n(dx_n)[\ell(\cdot,x_{n+1})]$  in the numerator that arises from $B_n(x_{n+1},dx_n)$. I think this should read $\phi_n(dx_n)\ell(x_n,x_{n+1})$  instead?\\
{\em The normalizing term given in the appendix is correct, see (2.10).}
\item p.30 Appendix A has $\phi_{0:n}L_{0,n}1_{X^n}$  in the denominator for  $\phi_{0:n+1}h$ which I think should read  $\phi_{0:n}L_{0,n}1_{X^{n+1}}$ as there is a dangling $dx_{n+1}$ otherwise.\\
{\em There was indeed a mistake in this identity, thank you for pointing this out. This was corrected using (2.3).}
\end{itemize}

### 2021-08-27 Bernoulli/glo-2020-prel.tex
Adjustment-multiplier weights

Assume for a moment that each transition density $\ud{n}$ is available in a closed form. Then standard SMC methods (see \cite{chopin:papaspiliopoulos:2020} for a recent introduction) can be used to approximate the distribution flows $(\post{0:n})_{n \in \nset}$ and $(\post{n})_{n \in \nset}$ using Monte Carlo samples generated recursively by means of sequential importance sampling and resampling operations. In order to set notations, let us recall the most general class of such algorithms, the so-called auxiliary particle filters \cite{pitt:shephard:1999}. In the light of Remark~\ref{we:vs:delmoral} it is enough to consider particle approximation of the marginals $(\post{n})_{n \in \nset}$. We proceed recursively and assume that we, at time $n \in \nset$, have at hand a sample $(\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N$ of $\Xset_n$-valued \emph{particles} (the $\epart{n}{i}$) and associated nonnegative importance weights (the $\ewght{n}{i}$) such that the self-normalised estimator $\post[\N]{n} h \eqdef \sumwght{n}^{-1} \sum_{i = 1}^\N \ewght{n}{i} h(\epart{n}{i})$, with $\sumwght{n} \eqdef \sum_{i = 1}^\N \ewght{n}{i}$, approximates $\post{n} h$ for every $\post{n}$-integrable function $h$. Then plugging $\post[\N]{n}$ into the recursion \eqref{eq:recursion:FK:marg} yields the approximation $\sum_{i = 1}^\N \pi_n(i, \rmd x)$ of $\post{n + 1}$, where 
\begin{equation} \label{eq:def:partmixt}
\partmixt_n(i, \rmd x) \propto \ewght{n}{i} \uk{n}(\epart{n}{i}, \rmd x)
\end{equation}
is a mixture distribution on $\powerset{\intvect{1}{\N}} \tensprod \Xfd_{n + 1}$. In order to form new particles approximating $\post{n + 1}$, we may draw, using importance sampling, pairs $(\ind{n + 1}{i}, \epart{n + 1}{i})_{i = 1}^\N$ of indices and particles from $\partmixt_n$ and discard the former. For this purpose, we introduce some instrumental mixture distribution 
\begin{equation} \label{eq:cond:instrumental:mixture}
\rho_n(i, \rmd x) \propto \ewght{n}{i} \adjfuncforward{n}(\epart{n}{i}) \, \prop{n}(\epart{n}{i}, \rmd x)
\end{equation}
on the same space, where $\adjfuncforward{n}$ is a real-valued positive \emph{adjustment-weight function} on $\Xset_n$ and $\prop{n}$ is a proposal kernel on $\Xset_n \times \Xfd_{n + 1}$ such that $\uk{n}(x, \cdot) \ll \prop{n}(x, \cdot)$ for all $x \in \Xset_n$. We will always assume that $\prop{n}$ has a transition density $\propdens{n}$ with respect to $\mu_{n + 1}$. A draw $(\ind{n + 1}{i}, \epart{n + 1}{i})$ from $\rho_n$ is easily generated by first drawing $\ind{n + 1}{i}$ from the categorical distribution induced by the adjusted importance weights and then drawing $\epart{n + 1}{i}$ by randomly moving the selected ancestor $\epart{n}{{\ind{n + 1}{i}}}$ according to the proposal kernel. These steps are often referred to as \emph{selection} and \emph{mutation}, respectively. 
Finally, each draw $\epart{n + 1}{i}$ is assigned the updated importance weight $\ewght{n + 1}{i}$ proportional to $\rmd \partmixt_n / \rmd \rho_n (\ind{n + 1}{i}, \epart{n + 1}{i})$, and the estimator $\post[\N]{n + 1} h = \sumwght{n + 1}^{-1} \sum_{i = 1}^\N \ewght{n + 1}{i} h(\epart{n + 1}{i})$ approximates $\post{n + 1} h$ for every $\post{n + 1}$-integrable $h$. The full update, which we will refer to as \emph{forward sampling} and express in a short form as
\begin{equation} \label{eq:forward:sampling}
    (\epart{n + 1}{i}, \ewght{n + 1}{i})_{i = 1}^\N \sim \mathsf{FS}((\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N),   
\end{equation}
is summarised in Algorithm~\ref{alg:ideal:SMC}.\footnote{Mathematically, the forward sampling operation defines a Markov transition kernel, which motivates the use of the symbol $\sim$ in \eqref{eq:forward:sampling}.}

>>>>

Assume for a moment that each transition density $\ud{n}$ is available in a closed form. Then standard SMC methods (see \cite{chopin:papaspiliopoulos:2020} for a recent introduction) can be used to approximate the distribution flows $(\post{0:n})_{n \in \nset}$ and $(\post{n})_{n \in \nset}$ using Monte Carlo samples generated recursively by means of sequential importance sampling and resampling operations. In order to set notations, let us recall the most general class of such algorithms, the so-called auxiliary particle filters \cite{pitt:shephard:1999}. In the light of Remark~\ref{we:vs:delmoral} it is enough to consider particle approximation of the marginals $(\post{n})_{n \in \nset}$. We proceed recursively and assume that we, at time $n \in \nset$, have at hand a sample $(\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N$ of $\Xset_n$-valued \emph{particles} (the $\epart{n}{i}$) and associated nonnegative importance weights (the $\ewght{n}{i}$) such that the self-normalised estimator $\post[\N]{n} h \eqdef \sumwght{n}^{-1} \sum_{i = 1}^\N \ewght{n}{i} h(\epart{n}{i})$, with $\sumwght{n} \eqdef \sum_{i = 1}^\N \ewght{n}{i}$, approximates $\post{n} h$ for every $\post{n}$-integrable function $h$. Then plugging $\post[\N]{n}$ into the recursion \eqref{eq:recursion:FK:marg} yields the approximation $\sum_{i = 1}^\N \pi_n(i, \rmd x)$ of $\post{n + 1}$, where 
\begin{equation} \label{eq:def:partmixt}
\partmixt_n(i, \rmd x) \propto \ewght{n}{i} \uk{n}(\epart{n}{i}, \rmd x)
\end{equation}
is a mixture distribution on $\powerset{\intvect{1}{\N}} \tensprod \Xfd_{n + 1}$. In order to form new particles approximating $\post{n + 1}$, we may draw, using importance sampling, pairs $(\ind{n + 1}{i}, \epart{n + 1}{i})_{i = 1}^\N$ of indices and particles from $\partmixt_n$ and discard the former. For this purpose, we introduce some instrumental mixture distribution 
\begin{equation} \label{eq:cond:instrumental:mixture}
\rho_n(i, \rmd x) \propto \ewght{n}{i} \adjfuncforward{n}(\epart{n}{i}) \, \prop{n}(\epart{n}{i}, \rmd x)
\end{equation}
on the same space, where $\adjfuncforward{n}$ is a real-valued positive \emph{adjustment-weight function} on $\Xset_n$ and $\prop{n}$ is a proposal kernel on $\Xset_n \times \Xfd_{n + 1}$ such that $\uk{n}(x, \cdot) \ll \prop{n}(x, \cdot)$ for all $x \in \Xset_n$. Adjustment multiplier weights were introduced in \cite{pitt:shephard:1999} to propose data-driven proposal distributions and design robust filtering estimates. These weights usually depend on the new observation and are often chosen to approximate the predictive likelihood of the new observation given the current particle. For further discussions see for instance \cite[Chapter~8]{Cappe:2005:IHM:1088883}.

We will always assume that $\prop{n}$ has a transition density $\propdens{n}$ with respect to $\mu_{n + 1}$. A draw $(\ind{n + 1}{i}, \epart{n + 1}{i})$ from $\rho_n$ is easily generated by first drawing $\ind{n + 1}{i}$ from the categorical distribution induced by the adjusted importance weights and then drawing $\epart{n + 1}{i}$ by randomly moving the selected ancestor $\epart{n}{{\ind{n + 1}{i}}}$ according to the proposal kernel. These steps are often referred to as \emph{selection} and \emph{mutation}, respectively. 
Finally, each draw $\epart{n + 1}{i}$ is assigned the updated importance weight $\ewght{n + 1}{i}$ proportional to $\rmd \partmixt_n / \rmd \rho_n (\ind{n + 1}{i}, \epart{n + 1}{i})$, and the estimator $\post[\N]{n + 1} h = \sumwght{n + 1}^{-1} \sum_{i = 1}^\N \ewght{n + 1}{i} h(\epart{n + 1}{i})$ approximates $\post{n + 1} h$ for every $\post{n + 1}$-integrable $h$. The full update, which we will refer to as \emph{forward sampling} and express in a short form as
\begin{equation} \label{eq:forward:sampling}
    (\epart{n + 1}{i}, \ewght{n + 1}{i})_{i = 1}^\N \sim \mathsf{FS}((\epart{n}{i}, \ewght{n}{i})_{i = 1}^\N),   
\end{equation}
is summarised in Algorithm~\ref{alg:ideal:SMC}.\footnote{Mathematically, the forward sampling operation defines a Markov transition kernel, which motivates the use of the symbol $\sim$ in \eqref{eq:forward:sampling}.}
